Consistent Polyhedral Surrogates via Embedding

### 2019-11-13 notes/top-k.tex
Added dual notes

\subsection{Notation and Assumptions}
\subsubsection{Notation}
We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-i} = \frac{1}{k-1} (k \bar u - u_{[i]})$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $i^{th}$ element, respectively.
$u[y]$ refers to the order of the $y^{th}$ component of $u$.
For example, if $u = (1,2,0)$, then $[2] = 1$. 
If $u$ is understand from context, we abuse notation to omit the $u$ and write $u[y] = [y]$.

@@

	If $[y] \geq k+1$, then 
	\begin{align*}
	L^{top-k}(u)_y &= (1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]})_+ \\
%	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
	&\geq \left(1 + \frac {1}{k} \sum_{i=1}^k (u' - e_y)_{[i]}\right)_+\\
	&= L^{top-k}(u')_y~.~
	\end{align*}
	The inequality comes from the equality of the first $k+1$ sorted elements of $u$ and $u'$, combined with setting $u_{[y]} \leq u'_{[y]} = 0$ in this case.

@@

>>>>

\subsection{Notation and Assumptions}
\subsubsection{Notation}
We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-i} = \frac{1}{k-1} (k \bar u - u_{[i]})$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $i^{th}$ element, respectively.
$u[y]$ refers to the order of the $y^{th}$ component of $u$.
For example, if $u = (1,2,0)$, then $u[2] = 1$. 
If $u$ is understood from context, we abuse notation to omit the $u$ and write $u[y] = [y]$.

@@

	If $[y] \geq k+1$, then 
	\begin{align*}
	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\right)_+ \\
%	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
	&\geq \left(1 + \frac {1}{k} \sum_{i=1}^k (u' - e_y)_{[i]}\right)_+\\
	&= L^{top-k}(u')_y~.~
	\end{align*}
	The inequality comes from the equality of the first $k+1$ sorted elements of $u$ and $u'$, combined with setting $u_{[y]} \leq u'_{[y]} = 0$ in this case.

@@

\section{Constructing a calibrated surrogate}
Here, we use the surrogate constructed in Proposition 2 of the paper to construct a calibrated surrogate for top $k$.
\subsection{$k=2$ and $n=3$}
First, we have $\risk{\ell}(p) = 1 - \min_y p_y$, and so $-\risk{\ell}(p) = \min_y p_y - 1$.
Taking the conjugate $(-\ell^*)(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \min_y p_y\}$, we see this is maximized by putting weight $1$ on $\argmax_y q_y$ and weight $0$ on every other element for $q \in \simplex$.
Since $n \neq 1$, we then have $\min_y p_y = 0$, so the conjugate of the negative risk reduces to $C(u) = 1 + \max_y u_y$.

Then, plugging this into our given loss yields $L(u)_y = 1 + u_{[1]} - u_y$.

\subsection{Generalizing $k$ and $n$}
Generalizing the above calibrated surrogate, we observe that $\risk(\ell) = 1 - \sum_{i=k+1}^n p_{[i]}$, and so $(-\risk{\ell})^*(q) = \sup_{p \in \simplex} \{\inprod p q + 1 - \sum_{i=k+1}^n p_{[i]}\}$.
This is maximized in the same way as above, and so we reduce this to $(-\risk{\ell})^*(q) = 1 - q_{[1]}$.

Again, we yield $L(u)_y = 1 + u_{[1]} - u_y$.
